CODE CHECK

### 2020-02-06 codecheck-paper.Rmd
Update codecheck-paper.Rmd

- https://medium.com/bits-and-behavior/a-modern-vision-for-peer-review-d5f73f0fae07 - work by Amy J. Ko: https://faculty.washington.edu/ajko/publications
  - is CODE CHECK's process too small, too incremental a change?
- _Successes and struggles with computational reproducibility: Lessons from the Fragile Families Challenge_ > https://osf.io/preprints/socarxiv/g3pdb/
- community standards for software, cf. slide 6 in https://figshare.com/articles/_/5675104
  - "good enough practice" is "get a colleague to try using it", slide 19 in https://figshare.com/articles/_/5675104
- journals doing code reviews
  - _"We know of 16 journals that take this valuable step (ie TOP Level 3): AEA as already mentioned, plus others in polisci, psychology, biostats, and org chem: see Data Rep Policies here https://t.co/plOF8j6ADU "_ (https://twitter.com/EvoMellor/status/1202692360456589339?s=09); see also whole thread!
  - https://medium.com/@NeurIPSConf/call-for-papers-689294418f43
  - https://www.journals.elsevier.com/information-systems/editorial-board/
  - SIGMOD Reproducibility Review?
  - Biostatistics "AER" (https://academic.oup.com/biostatistics/article/10/3/405/293660)
- open science platforms/cloud services > https://www.nature.com/articles/d41586-019-03366-x
- live code in articles > o2r, eLife RDS https://www.nature.com/articles/d41586-019-00724-7, ...
- Artefact Evaluation - https://www.artifact-eval.org/about.html
- continuous analysis - https://www.nature.com/articles/nbt.3780

>>>>

- https://medium.com/bits-and-behavior/a-modern-vision-for-peer-review-d5f73f0fae07 - work by Amy J. Ko: https://faculty.washington.edu/ajko/publications
  - is CODE CHECK's process too small, too incremental a change?
- _Successes and struggles with computational reproducibility: Lessons from the Fragile Families Challenge_ > https://osf.io/preprints/socarxiv/g3pdb/
- community standards for software, cf. slide 6 in https://figshare.com/articles/_/5675104
  - "good enough practice" is "get a colleague to try using it", slide 19 in https://figshare.com/articles/_/5675104
- journals doing code reviews
  - _"We know of 16 journals that take this valuable step (ie TOP Level 3): AEA as already mentioned, plus others in polisci, psychology, biostats, and org chem: see Data Rep Policies here https://t.co/plOF8j6ADU "_ (https://twitter.com/EvoMellor/status/1202692360456589339?s=09); see also whole thread!
  - https://medium.com/@NeurIPSConf/call-for-papers-689294418f43
  - https://www.journals.elsevier.com/information-systems/editorial-board/
  - SIGMOD Reproducibility Review?
  - Biostatistics "AER" (https://academic.oup.com/biostatistics/article/10/3/405/293660)
- open science platforms/cloud services > https://www.nature.com/articles/d41586-019-03366-x
- live code in articles > o2r, eLife RDS https://www.nature.com/articles/d41586-019-00724-7, ...
- Artefact Evaluation - https://www.artifact-eval.org/about.html
- continuous analysis - https://www.nature.com/articles/nbt.3780
- "A Universal Identifier for Computational Results" > https://www.sciencedirect.com/science/article/pii/S1877050911001256
- Discussion about using Docker containers during JOSS reviews > https://github.com/openjournals/joss/issues/498#issuecomment-462046912
